Research Cases

### 2025-10-19 Code/R/Research/cases_research.Rmd
4-channel signals with different 3-ranks

@@

```{r}
# If parameters are matrices, then a multivariate series will be constructed.
# In this parameters matrices columns correspond to series and rows to summands
# This means, if you want to increase number of ts in a sum, you grow rows,
# and if you want to add a 1d ts to a mv ts, you grow columns.
# The results is either a 1d ts, or a matrix, where each column is a 1d ts.
construct_periodics <- function(N,
                                ampl,
                                rate,
                                freq,
                                phase,
                                complex = TRUE,
                                from = 0,
                                by = 1) {
  if (any(c(length(ampl), length(rate), length(freq)) != length(phase))) {
    stop("Amplitudes, rates, frequencies and phases all must have the same length")
  }
  if (all(is.matrix(ampl), is.matrix(rate), is.matrix(freq), is.matrix(phase))) {
    if (any(c(dim(ampl), dim(rate), dim(freq)) != dim(phase))) {
      stop("Amplitudes, rates, frequencies and phases all must have the same dimensions")
    }
  } else if (any(is.matrix(ampl), is.matrix(rate), is.matrix(freq), is.matrix(phase))) {
    stop("All parameters should be either matrices, or vectors at the same time")
  }

@@

## Parameters for mv series (P = 2)
```{r}
P <- 2
P_case <- "2s"

# no rates
rates.true <- matrix(c(0, 0, 0, 0), ncol = P)
rates_case <- "_nr"
# small equal rated
# rates.true <- matrix(c(-0.01, -0.01, -0.01, -0.01), ncol = P)
# rates_case <- "_ser"
# large equal rates
# rates.true <- matrix(c(-0.02, -0.02, -0.02, -0.02), ncol = P)
# rates_case <- "_ler"
# different by summands rates
# rates.true <- matrix(c(-0.01, -0.01, -0.02, -0.02), ncol = P)
# rates_case <- "_dsr"
# different by time series rates
# rates.true <- matrix(c(-0.01, -0.02, -0.01, -0.02), ncol = P)
# rates_case <- "_dtr"
# different rates
# rates.true <- matrix(c(-0.01, -0.02, -0.015, -0.025), ncol = P)
# rates_case <- "_dr"

# no freqs
# freqs.true <- matrix(c(0, 0, 0, 0), ncol = P)
# freqs_case <- "_nf"
# different by summands freqs
freqs.true <- matrix(c(0.2, 0.2, 0.22, 0.22), ncol = P)
freqs_case <- "_dsf"
# different by time series freqs
# freqs.true <- matrix(c(0.2, 0.22, 0.2, 0.22), ncol = P)
# freqs_case <- "_dtf"
# different freqs
# freqs.true <- matrix(c(0.2, 0.22, 0.18, 0.24), ncol = P)
# freqs_case <- "_df"
# close different by summands freqs
# freqs.true <- matrix(c(0.02, 0.02, 0.0205, 0.0205), ncol = P)
# freqs_case <- "_cdsf"

# equal amplitudes
# A <- matrix(c(1, 1, 1, 1), ncol = P)
# A_case <- "_ea"
# different by summands amplitudes 
# A <- matrix(c(1, 2, 1, 2), ncol = P)
# A_case <- "_dsa"
# different by summands, proportional by ts amplitudes 
A <- matrix(c(1, 2, 3, 6), ncol = P)
A_case <- "_dspta"
# different amplitudes
# A <- matrix(c(1, 2, 1.5, 2.5), ncol = P)
# A_case <- "_da"

# equal phases
phases.true <- matrix(c(0, 0, 0, 0), ncol = P)
phases_case <- "_ep"
# different by time series phases
# phases.true <- matrix(c(0, pi / 3, 0, pi / 3), ncol = P)
# phases_case <- "_dtp"

complex.signal <- TRUE
complex_case <- "_c" # complex
# complex.signal <- FALSE
# complex_case <- "_r" # real

@@

```{r}
full_case <- paste0(n_case, rates_case, freqs_case, A_case, phases_case, complex_case)
max.r <- calc_rank(A, rates.true, freqs.true, phases.true, complex.signal)

@@

if (is.matrix(signal)) {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics_mv", full_case, ".RData"))
} else {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics", full_case, ".RData"))
}
```

@@

```{r}
# load()
```

>>>>

# Setup

@@

```{r}
# If parameters are matrices, then a multivariate series will be constructed.
# In this parameters matrices columns correspond to summnands and rows to channels
# This means, if you want to increase number of ts in a sum, you grow columns,
# and if you want to add a channel to an mv ts, you grow rows
# The results is either a 1d ts, or a matrix, where each column is a 1d ts -- channel.
construct_periodics <- function(N,
                                ampl,
                                rate,
                                freq,
                                phase,
                                complex = TRUE,
                                from = 0,
                                by = 1) {
  if (any(c(length(ampl), length(rate), length(freq)) != length(phase))) {
    stop("Amplitudes, rates, frequencies and phases all must have the same length")
  }
  if (all(is.matrix(ampl), is.matrix(rate), is.matrix(freq), is.matrix(phase))) {
    if (any(c(dim(ampl), dim(rate), dim(freq)) != dim(phase))) {
      stop("Amplitudes, rates, frequencies and phases all must have the same dimensions")
    }
  } else if (any(is.matrix(ampl), is.matrix(rate), is.matrix(freq), is.matrix(phase))) {
    stop("All parameters should be either matrices, or vectors at the same time")
  }

@@

## Parameters for mv series (P = 2)
```{r}
P <- 2

# no rates
# rates.true <- matrix(c(0, 0, 0, 0), nrow = P)
# rates_case <- "_nr"
# small equal rated
# rates.true <- matrix(c(-0.01, -0.01, -0.01, -0.01), nrow = P)
# rates_case <- "_ser"
# large equal rates
# rates.true <- matrix(c(-0.02, -0.02, -0.02, -0.02), nrow = P)
# rates_case <- "_ler"
# different by summands rates
# rates.true <- matrix(c(-0.01, -0.01, -0.02, -0.02), nrow = P)
# rates_case <- "_dsr"
# different by time series rates
rates.true <- matrix(c(-0.01, -0.02, -0.01, -0.02), nrow = P)
rates_case <- "_dtr"
# different rates
# rates.true <- matrix(c(-0.01, -0.02, -0.015, -0.025), nrow = P)
# rates_case <- "_dr"

# no freqs
# freqs.true <- matrix(c(0, 0, 0, 0), nrow = P)
# freqs_case <- "_nf"
# different by summands freqs
# freqs.true <- matrix(c(0.2, 0.2, 0.22, 0.22), nrow = P)
# freqs_case <- "_dsf"
# different by time series freqs
freqs.true <- matrix(c(0.2, 0.22, 0.2, 0.22), nrow = P)
freqs_case <- "_dtf"
# different freqs
# freqs.true <- matrix(c(0.2, 0.22, 0.18, 0.24), nrow = P)
# freqs_case <- "_df"
# close different by summands freqs
# freqs.true <- matrix(c(0.02, 0.02, 0.0205, 0.0205), nrow = P)
# freqs_case <- "_cdsf"

# equal amplitudes
A <- matrix(c(1, 1, 1, 1), nrow = P)
A_case <- "_ea"
# different by summands amplitudes 
# A <- matrix(c(1, 2, 1, 2), nrow = P)
# A_case <- "_dsa"
# different by summands, proportional by ts amplitudes 
# A <- matrix(c(1, 2, 3, 6), nrow = P)
# A_case <- "_dspta"
# different amplitudes
# A <- matrix(c(1, 2, 1.5, 2.5), nrow = P)
# A_case <- "_da"

# equal phases
phases.true <- matrix(c(0, 0, 0, 0), nrow = P)
phases_case <- "_ep"
# different by time series phases
# phases.true <- matrix(c(0, pi / 3, 0, pi / 3), nrow = P)
# phases_case <- "_dtp"

@@

## Parameters for mv series (P = 4)
```{r}
P <- 4
P_case <- "_c4"

# no rates
# rates.true <- matrix(c(0, 0, 0, 0), nrow = P)
# rates_case <- "_nr"
# small equal rated
# rates.true <- matrix(c(-0.01, -0.01, -0.01, -0.01), nrow = P)
# rates_case <- "_ser"
# large equal rates
# rates.true <- matrix(c(-0.02, -0.02, -0.02, -0.02), nrow = P)
# rates_case <- "_ler"
# different by summands rates
# rates.true <- matrix(c(-0.01, -0.01, -0.02, -0.02), nrow = P)
# rates_case <- "_dsr"
# different by time series rates
# rates.true <- matrix(rep(c(-0.01, -0.02), P), nrow = P)
# rates_case <- "_dtr"
rates.true <- matrix(rep(c(-0.01, -0.02, -0.03, -0.04), P), nrow = P)
rates_case <- "_dtr"
# different rates
# rates.true <- matrix(c(-0.01, -0.02, -0.015, -0.025), nrow = P)
# rates_case <- "_dr"

# no freqs
# freqs.true <- matrix(c(0, 0, 0, 0), nrow = P)
# freqs_case <- "_nf"
# different by summands freqs
# freqs.true <- matrix(c(0.2, 0.2, 0.22, 0.22), nrow = P)
# freqs_case <- "_dsf"
# different by time series freqs
# freqs.true <- matrix(rep(c(0.2, 0.22), P), nrow = P)
# freqs_case <- "_dtf"
freqs.true <- matrix(rep(c(0.2, 0.22, 0.24, 0.26), P), nrow = P)
freqs_case <- "_dtf"
# different freqs
# freqs.true <- matrix(c(0.2, 0.22, 0.18, 0.24), nrow = P)
# freqs_case <- "_df"
# close different by summands freqs
# freqs.true <- matrix(c(0.02, 0.02, 0.0205, 0.0205), nrow = P)
# freqs_case <- "_cdsf"

# equal amplitudes
# A <- matrix(rep(1, P * 2), nrow = P)
# A_case <- "_ea"
A <- matrix(rep(1, P * 4), nrow = P)
A_case <- "_ea"
# different by summands amplitudes 
# A <- matrix(c(1, 2, 1, 2), nrow = P)
# A_case <- "_dsa"
# different by summands, proportional by ts amplitudes 
# A <- matrix(c(1, 2, 3, 6), nrow = P)
# A_case <- "_dspta"
# different amplitudes
# A <- matrix(c(1, 2, 1.5, 2.5), nrow = P)
# A_case <- "_da"

# equal phases
# phases.true <- matrix(rep(0, P * 2), nrow = P)
# phases_case <- "_ep"
phases.true <- matrix(rep(0, P * 4), nrow = P)
phases_case <- "_ep"
# different by time series phases
# phases.true <- matrix(c(0, pi / 3, 0, pi / 3), nrow = P)
# phases_case <- "_dtp"

## Constructing Signal

```{r}
full_case <- paste0(n_case, P_case, rates_case, freqs_case, A_case, phases_case, complex_case)
max.r <- calc_rank(A, rates.true, freqs.true, phases.true, complex.signal)

@@

if (is.matrix(signal)) {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/four_periodics_mv", full_case, ".RData"))
} else {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics", full_case, ".RData"))
}
```

@@

# Results
```{r}
# load()
```
